An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
cleaner algorithm

    Input: $C$ contains intermediate representations\\ 
     \qquad \enspace \enspace of configuration files\\

    \For{each file $F$ in $C$}
      \For{each $\tau \in \theta$}
        \State $R = \{\}$
        \State $Q = filter(F,\tau)$ 
        \State // $Q$ contains entries in $F$ with $\tau$ in type list
        \For{each entry $e$ in $Q$}
               \If{$g(e)$ is false}
                        \State continue to next entry
                        \Else \enspace $R = R  \cup  \textrm{constructRules}(e, \tau, Q)$
               \EndIf
                        %Check if $t$ is satisfied  over rest 
        \EndFor
     \State Update $p_{\tau}$ appropriately
     \EndFor
    \EndFor
  \end{algorithmic}
\end{algorithm}

%                \For{$\tau \in typelist(e)$}
%                        \For{$t \in templates(\tau)$}
%                        \If{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
%                                        \State update $p_{\tau}$ appropriately
%                                \ElsIf{anti($t$) is satisfied over rest of entries}
%                                        \State update $p_{\tau}$ appropriately
%                                \EndIf

\begin{algorithm}
\caption{constructRules}
  \begin{algorithmic}[1]
  \State \textbf{constructRules}($e, \tau, Q$):\\
    Input: entry $e$ from intermediate representation\\ 
     \qquad \enspace \enspace type $\tau$\\
     \qquad \enspace \enspace set of entries $Q$\\
     $R = \{\}$
     \For{each $t \in templates(\tau)$}
      \State Let $P$ be the set of permutations of distinct entries from $Q$, with arity of $t$, containing $e$
      \For{each $p \in P$}
%      \State Let an entry in $D$ be represented by $(e, e_1, e_2, \ldots)$
      \State Construct the rule $r$ corresponding to $t(v(e_1), v(e_2), \ldots, v(e), \ldots, v(e_{n-1}), v(e_n))$.
      \If{$r$ is satisfied}
        $R = R \cup r$
      \EndIf
     \EndFor
     \EndFor
     \State return $R$
  \end{algorithmic}
\end{algorithm}

>>>>

  Input: set $C$ contains intermediate representations\\ 
     \qquad \enspace \enspace of configuration files\\

    \State $R = \{\}$ // denotes rule set
    \State $P$ // denotes probabilities associated with rule set
    \For{each file $F$ in $C$}
      \For{each $\tau \in \theta$}
        \State $Q = filter(F,\tau)$ 
        \State // $Q$ contains entries in $F$ with $\tau$ in type list
        \State $RM$ contains entries in remove set
        \For{each entry $e$ in $Q$}
               \If{$g(e)$ is false}
                        \State continue to next entry
                        \Else \enspace $CR = \textrm{constructRules}(e, \tau, Q \backslash RM)$
                        \State $R = R  \cup CR$
                        \State For each $r \in CR$, update $P$ 
               \EndIf
               \State $RM = RM \cup e$
        \EndFor
     \EndFor
    \EndFor
    \State Based on $P$, accept rules in $R$ according to threshold. 
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{constructRules}
  \begin{algorithmic}[1]
  \State \textbf{constructRules}($e, \tau, S$):\\
    Input: entry $e$ from intermediate representation\\ 
     \qquad \enspace \enspace type $\tau$\\
     \qquad \enspace \enspace set of entries $S$\\
     $R = \{\}$
     \For{each $t \in templates(\tau)$}
        \State Let $n$ be the arity of $t$
        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
        \For{each $p \in P$}
         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
           \For{$i = 1:n$}
           \State Create a $n$-tuple by placing $e$ at the $i$-th place and filling the remaining entries with $p$, in order. Let this $n$-tuple be $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
           \State $r = \textrm{constructRule}(u)$ 
            \If{$r$ is satisfied}
              $R = R \cup r$
            \EndIf
          \EndFor
        \EndFor
     \EndFor
     \State return $R$
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{constructRule}
  \begin{algorithmic}[1]
  \State \textbf{constructRule}($u$):\\
  Input: a tuple of entries, $u$, denoted by $(e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$ \\
    \State return $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$.
  \end{algorithmic}
\end{algorithm}
